# Exporation of QC matrix for Geuvadis

Read in the matrix and re-assign levels of the operator (the center
which performed sequencing). 

```{r}
file <- "../qcstats/GD667.QCstats.txt"
library(readr)
qc <- read_delim(file,"\t")
means <- sapply(split(qc$GC_hist_bins_70, qc$Operator), mean)
o <- order(means)
qc$Operator <- factor(qc$Operator)
qc$Operator <- factor(qc$Operator, levels=levels(qc$Operator)[o])
lvls <- levels(qc$Operator)
levels(qc$Operator)[lvls == "MPIMG_S_DOKEL"] <- "MPIMG"
```

# Boxplot of who is missing high GC content reads

```{r}
for (i in 12:19) {
  boxplot(qc[[paste0("GC_hist_bins_",i*5)]] ~ qc$Operator,
          las=3)
  legend("topleft",legend=paste0("GC=",i*5),bty="n",pch=NA,cex=2)
}
```

# Pick a measure for missingness and look at other variables

GC at 75% is a good indicator for missingness, and is used below as
the primary variable to try to find correlates.

Lots of variables:

```{r}
substr(colnames(qc),1,20)
```

# Variables that correlate with GC missing

The variables which correlate most are confounded with operator. So we
definitely can't say if these are causative variables, or just
something which is confounded with the real explantory factor.

```{r}
library(RColorBrewer)
palette(c(brewer.pal(5, "Dark2"),brewer.pal(6, "Pastel1")))
with(qc, plot(GC_hist_bins_75, Operator,
              col=Operator, pch=16))
with(qc, plot(GC_hist_bins_75, LibraryConcentration_ng.ul,
              col=Operator, pch=16))
with(qc, plot(GC_hist_bins_75, BioanalyzerSize_bp,
              col=Operator, pch=16))
with(qc, plot(GC_hist_bins_75, INSERT_SIZE_MODE,
              col=Operator, pch=16))
```

# Other numeric variables

Other numeric variables which seem to have no relationship:

```{r}
with(qc, plot(GC_hist_bins_75, RIN, col=Operator, pch=16))
with(qc, plot(GC_hist_bins_75, RNAConcentration_ng.ul,
              col=Operator, pch=16))
with(qc, plot(GC_hist_bins_75, RNAVolumeShipped_ul,
              col=Operator, pch=16))
with(qc, plot(GC_hist_bins_75, RNAQuantityShipped_ug,
              col=Operator, pch=16))
with(qc, plot(GC_hist_bins_75, LibraryQuantitySequencing_pM,
              col=Operator, pch=16))
with(qc, plot(GC_hist_bins_75,
              12 * (as.numeric(substr(SequencingDate,2,3)) - 11) + 
              31 * as.numeric(substr(SequencingDate,4,5)) +
              as.numeric(substr(SequencingDate,6,7)),
              col=Operator, pch=16, ylab="days since 1/1/2011"))
with(qc, plot(GC_hist_bins_75, Total_read,
              col=Operator, pch=16))
with(qc, plot(GC_hist_bins_75, TOTAL_EXONIC_OVER_TOTAL_READS,
              col=Operator, pch=16))
with(qc, plot(GC_hist_bins_75, Number_of_unique_15mers,
              col=Operator, pch=16))
with(qc, plot(GC_hist_bins_75, Qual_mean,
              col=Operator, pch=16))
with(qc, plot(GC_hist_bins_75, Qual_median,
              col=Operator, pch=16))
```

# Categorical variables

Categorical variables are either confounded or have no apparent relationship:

```{r}
with(qc, plot(GC_hist_bins_75, factor(Machine),
              col=Operator, pch=16))
with(qc, plot(GC_hist_bins_75, factor(FlowCell),
              col=Operator, pch=16))
with(qc, plot(GC_hist_bins_75, factor(Lane),
              col=Operator, pch=16))
with(qc, plot(GC_hist_bins_75, factor(LibraryPrepPlate),
              col=Operator, pch=16))
with(qc, plot(GC_hist_bins_75, factor(LibraryPrepKitBatch),
              col=Operator, pch=16))
with(qc, plot(GC_hist_bins_75, factor(ClusterKitBatch),
              col=Operator, pch=16))
with(qc, plot(GC_hist_bins_75, factor(SequencingKitBatch),
              col=Operator, pch=16))
with(qc, plot(GC_hist_bins_75, factor(LibraryConcentrationMethod),
              col=Operator, pch=16))
```
